OA Share

### 2020-12-09 analysis/006_license.Rmd
export data
bugfix regex

>>>>

### License for Mirror journals

```{sql, connection=con, output.var="els_yearly_mirror"}
SELECT  issued_year,
        container_title,
        COUNT(DISTINCT(doi)) as all_articles 
    FROM
        `api-project-764811344545.cr_dump_march_20.els_all_may_20`
    WHERE
        issued_year > 2014 
        and issued_year < 2020        
        and not    regexp_contains(title,'^Author Index$|^Back Cover|^Contents$|^Contents:|^Cover Image|^Cover Picture|^Editorial Board|^Front Cover|^Frontispiece|^Inside Back Cover|^Inside Cover|^Inside Front Cover|^Issue Information|^List of contents|^Masthead|^Title page|^Correction$|^Corrections to|^Corrections$|^Withdrawn')
        and (not regexp_contains(page, '^S') or page is NULL)
        and regexp_contains(container_title, ' X$')
    GROUP BY
        issued_year,
        container_title
```

```{r}
els_yearly_mirror
```

```{r}
sum(els_yearly_mirror$all_articles)
length(unique(els_yearly_mirror$container_title))
write_csv(els_yearly_mirror, here::here("data", "x_journals_volume.csv"))
```
